Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective \titlenote{(Produces the permission block, and copyright information). For use with SIG-ALTERNATE.CLS. Supported by ACM.}

### 2015-04-30 thesis/acm/paper.tex
Added note to conclusion
Added note to 3rd party section

\subsubsection{3\textsuperscript{rd} Party}

@@

(!!!We are waiting for more information from Johanna to confirm / add to this section!!!)

@@

\section{Conclusion RQ2} \label{conclusion}

>>>>

\subsubsection{3\textsuperscript{rd} Party}
ATTN: (!!!We are waiting for more information from Johanna to confirm / add to this section!!!)

@@

@@

\section{Conclusion} \label{conclusion}
ATTN: This section has not been started.
